% LaTeX resume using res.cls
\documentclass[line,margin]{res}
% \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
% \usepackage{tgpagella}
\usepackage{palatino}

\usepackage{hyperref}  % hyperlinks
\usepackage{enumitem}  % itemize options

% \addtolength{\hoffset}{-0.5cm}
% \addtolength{\textwidth}{1cm}
% \addtolength{\voffset}{-2.5cm}
% \addtolength{\textheight}{5cm}

\setlist[itemize]{label={\small\textbullet}, itemsep=-2pt, leftmargin=4.5mm}

\newcommand{\experience}[3]{\textbf{#1}, \textit{#2} \hfill #3 \\ \vspace{-4mm}}
\newcommand{\ura}[3]{Advisor(s): \textbf{#1}, \textit{#2} \hfill #3 \\ \vspace{-4mm}}
\newcommand{\paper}[6]{\href{#6}{#1. #2. In \textit{#3}, #4, #5.}}
\newcommand{\software}[3]{\href{#3}{\textbf{#1: } #2.}\vspace{-2mm}}
\newcommand{\talk}[4]{#1. \textit{#2}, #4. \vspace{-2mm}}
\newcommand{\award}[2]{#1 \hfill #2}


\begin{document}

\name{\Large{Nicholas Vadivelu - Curriculum Vitae}}
\address{
    % (647) 643-4450 $\cdot$
    \href{mailto:nicholas.vadivelu@gmail.come}{nicholas.vadivelu@gmail.com} $\cdot$
    \href{https://nicholasvadivelu.com/}{nicholasvadivelu.com}
}

\begin{resume}
\vspace{-4mm}

\section{EDUCATION}
    \textit{Bachelor of Mathematics}, Computer Science \& Statistics (Double Major) \hfill 2017 - 2022 \\
    University of Waterloo, Waterloo, ON, \\
    Cumulative GPA: 3.94/4.00


\section{EXPERIENCE}
    \experience{Citadel}{Quantitative Research Intern}{Jun - Dec 2021}
    \begin{itemize}
        \item Researched transfer learning and out-of-domain generalization to predict user behaviour and demographics between datasets of different modalities (under NDA).
    \end{itemize}

    \experience{NVIDIA}{Performance Software Engineering Intern}{Aug - Dec 2020}
    \begin{itemize}
        \item Reduced BERT/Megatron \textbf{inference latency by ~30\%} through sparsity (C++).
        \item Open-sourced sparse BERT (Python), the current fastest inference implementation.
    \end{itemize}

    \experience{Uber ATG}{Research Intern}{Jan - Aug 2020}
    \begin{itemize}
        \item Improved \textbf{object detection by 90\%} (AP) and \textbf{motion forecasting by 22\%} (L2) of a self-driving neural net under realistic positional error.
        \item Published the learned positional error correction system at CoRL (first author).
    \end{itemize}

    \experience{Google Brain}{Research Software Engineering Intern}{May - Aug 2019}
    \begin{itemize}
        \item Unlocked K-FAC for \textbf{over 370,000 users} by implementing and open-sourcing automatic support for arbitrary neural network architectures (Keras).
        \item Enabled trivial multi-node training with efficient distributed operation placement.
        \item Designed, created, and open-sourced idiomatic, reproducible training recipes.
    \end{itemize}

    \experience{John Hancock Financial}{Data Science Intern}{May - Aug 2018}
    \begin{itemize}
        \item Achieved a \textbf{fraud detection rate of 63\%} by designing an unsupervised ML model.
        \item Deployed 25 fraud heuristics that \textbf{correctly flagged 100+} fraudulent claims.
    \end{itemize}

    \experience{Sunnybrook Research Institute}{Software Developer Intern}{Jul - Aug 2017}
    \begin{itemize}
        \item Improved MRI segmentation accuracy by \textbf{up to 80\%} and reduced time to contour MRI scans from \textbf{{\raise.17ex\hbox{$\scriptstyle\sim$}} 5 hrs to {\raise.17ex\hbox{$\scriptstyle\sim$}} 40 mins}; Acknowledged in \href{https://aapm.onlinelibrary.wiley.com/doi/epdf/10.1002/mp.15263}{Hyvärinen et al, 2021}
    \end{itemize}

    \experience{McMaster University}{Research Intern}{Jul - Aug 2016}
    \begin{itemize}
        \item Collected, analyzed, and presented research on photoluminescence data; Acknowledged in \href{https://www.bradleyresearchgroup.ca/publications.html#:~:text=J.%20W.%20Miller%2C%20D,Photonics%20North%2C%20paper%2015.20.}{Miller et al, 2017}.
    \end{itemize}

\section{RESEARCH}
    \ura{Prof. Martin Lysy, Dr. Lawrence Murray}{}{Winter 2021}
    \begin{itemize}
        \item Research in Sequential Monte Carlo methods for inference on COVID models.
    \end{itemize}
    \vspace{-2mm}

    \ura{Prof. Gautam Kamath}{}{Fall 2020}
    \begin{itemize}
        \item Research in computationally efficient differentially private SGD.
    \end{itemize}
    \vspace{-2mm}

    \ura{Prof. Pascal Poupart}{}{Fall 2019}
    \begin{itemize}
        \item Research in practical second-order methods for neural network optimization.
    \end{itemize}
    \vspace{-2mm}

    \ura{Prof. Pascal Poupart}{}{Winter 2019}
    \begin{itemize}
        \item Research in deep learning-based methods to identify bugs in source code.
    \end{itemize}
    \vspace{-2mm}

\newpage

\section{PUBLICATIONS}
    \small{(* = equal contribution)} \vspace{2mm} \\
    \paper
    {Pranav Subramani*, \textbf{Nicholas Vadivelu*}, Gautam Kamath}
    {Enabling Fast Differentially Private SGD via Just-in-Time Compilation and Vectorization}
    {Conference on Neural Information Processing Systems (NeurIPS)}{Virtual}{2021}
    {https://arxiv.org/abs/2010.09063}

    \paper
    {\textbf{Nicholas Vadivelu}, Mengye Ren, James Tu, Jingkang Wang, Raquel Urtasun}
    {Learning to Communicate and Correct Pose Errors}
    {Conference on Robot Learning (CoRL)}{Virtual}{2020}
    {https://arxiv.org/abs/2011.05289}
    % \vspace{-3mm}


\section{SOFTWARE}
    \software{ShapeCheck}{Framework agnostic runtime array checking library}
    {https://github.com/n2cholas/jax-resnet}

    \software
    {JAX ResNet}{Composable, unit-tested code and checkpoints for ResNet variants}
    {https://pypi.org/project/shapecheck/}

    Contributed to: TensorFlow, PyTorch Ignite, Optax, Flax.

\section{LEADERHIP \& ACTIVITIES}
    \experience{Math Faculty}{Peer Mentor}{Jan 2021 - Present} \\
    \experience{Tech+}{Mentor}{Jan 2019 - Present} \\
    \experience{Technical Blog}{\href{https://nicholasvadivelu.com/}{nicholasvadivelu.com}}{Sep 2018 - Present} \\
    \experience{UWaterloo Data Science Club}{Lecturer}{Sep 2018 - Present} \\
    \experience{Hack the North}{Mentor/Workshop Lead}{Sep 2018, 2019} \\
    \experience{WATonomous}{Computer Vision Developer}{Sep 2017 - Apr 2018}

\section{AWARDS}
    \award{\href{https://cs.uwaterloo.ca/news/nicholas-vadivelu-receives-2021-jessie-w-h-zou-memorial-award}{Jessie W.H. Zou Memorial Award} (Top Undergrad Researcher in CS Department)}{2021}\\
    \award{President's Research Award (\$1500)}{2020}\\
    \award{David Shepherd Upper-Year Scholarship in Mathematics (\$5000)}{2019}\\
    \award{President's Research Award (\$1500)}{2019}\\
    \award{Faculty of Mathematics Scholarship (\$5000)}{2018}\\
    \award{University of Waterloo President's Scholarship of Distinction (\$1500)}{2018}\\
    \award{Fahd Ananta Fellowship Award in Computer Science (\$200)}{2017}
    % \award{Lieutenant Governor's Community Volunteer Award}{2017}

\section{TALKS}
    \talk
    {Clustering for Image Analysis (with Kanika Chopra)}
    {WiSTEM High School Student Conference}{Virtual}{Feb 2021}

    \talk
    {Establishing a Productive ML Research Workflow}
    {Hack the North++}{Virtual}{Jan 2021}

    \talk
    {Interactive Data Visualization with Altair}
    {Hack the North++}{Virtual}{Jan 2021}

    \talk
    {Overview of Data Science and Data Science Careers}
    {UWaterloo Data Science Club}{Waterloo}{Aug 2020}

    \talk
    {What You See is What You Get: Exploiting Visibility for 3D Object Detection}
    {Uber ATG Reading Group}{Toronto}{Jul 2020}

    \talk
    {Introduction to JAX for Machine Learning and More}
    {University of Waterloo Data Science Club}{Waterloo}{Jul 2020}

    \talk
    {Stand-Alone Self-Attention in Vision Models}
    {Uber ATG Reading Group}{Toronto}{Apr 2020}

    \talk
    {Neural Network Optimization Methods}
    {Reading Group}{Waterloo}{Dec 2019}

    \talk
    {Introduction to Neural Networks in TensorFlow 2.0}
    {Laurier Developer Student Club}{Waterloo}{Nov 2019}

    \talk
    {Introduction to Machine Learning with Scikit-learn}
    {Hack the North}{Waterloo}{Sep 2019}

    \talk
    {Introduction to Data Cleaning with Pandas}
    {Hack the North}{Waterloo}{Sep 2019}

\end{resume}
\end{document}
